### 2019-11-28 README.Rmd
some

# _gosset_: Modelling Metadata and Experimental Citizen Science <img align="right" src="man/figures/logo.png">

Package website: https://agrobioinfoservices.github.io/gosset/

@@

The **gosset** package provides an environment for modelling metadata and experimental citizen science data. It has implementations of cross-validation and stepwise variable selection for glm, lm, Bradley-Terry and Plackett-Luce models.

>>>>

# *gosset*: Modelling Metadata and Experimental Citizen Science <img align="right" src="man/figures/logo.png">

@@

The **gosset** package provides an environment for modelling metadata and experimental citizen science data.
